Gravitational wave sources in our Galactic backyard: Predictions for BH and NS binaries in LISA

### 2021-06-20 paper/tex/sections/discussion.tex
proofread the simple mw subsection

\subsection{Assessing the effect of an improved Milky Way model}
In this section, we repeat our analysis using a simpler model for the Milky Way in order to assess the effect of using a metallicity-dependent Milky Way model. For this purpose, we use model for the Milky Way used in \citet{Breivik+2020} as this is representative of the models used in previous works.

Their model can be summarised as follows: it is made up of three components, a thin disc, a thick disc and a bulge. The spatial distributions and relative masses for these components are given in \citet{McMillan+2011}. \citet{Breivik+2020} assume constant star formation over 10 Gyr for the thin disc, a 1 Gyr burst of star formation 11 Gyr ago for the thick disc and a 1 Gyr burst of star formation 10 Gyr ago for the bulge. Most differently, only two metallicities are used and assigned independent of age or position. Binaries formed in the thin disc and bulge are assumed to have a metallicity of $Z = 0.02$ and those formed in the thick disc are assumed to have $Z = 0.003$.

We show this model in Fig.~\ref{fig:simple_mw} in the same form as Fig.~\ref{fig:galaxy_schematic} for ease of comparison between our models. The two major differences we can see in these plots is that the \citet{Breivik+2020} model is more centrally concentrated and only has two fixed metallicity populations. In addition, though it can't be seen in these plots, the simpler prescriptions for the birth times mean that the star formation history is highly discontinuous at $\tau = 9 \unit{Gyr}$ and much more star formation occurs from $\tau = 9 \unit{Gyr}$ to $\tau = 11 \unit{Gyr}$.

@@

We find that using this simpler Milky Way model with our fiducial physics assumptions (model \modFid{}), the expected number of detections for BHBHs, BHNSs and NSNSs for a 4-year LISA mission is $39$, $39$ and $14$ respectively. Thus the BHBH and BHNS detection rates are only marginally increased but the NSNS detection is overestimated by nearly a factor of 2.

Moreover, the distribution of parameters within the population, especially the mass distributions are notably disparate. By using only two fixed metallicity populations, unphysical artifacts are introduced into distribution of DCO masses (Kummer at al. (in prep)). For example, in Fig.~\ref{fig:bh_mass_simple_mw}, we show the black hole mass distribution produced by the simulation using the simple Milky Way model. Despite the fact that these KDEs use the same bandwidth as Fig.~\ref{fig:fiducial_pdf_distributions}, the distributions show many more sharp transitions, which is a result of pileups occurring at specific masses for specific metallicities. Moreover, the lack of lower metallicities systems means that higher mass systems are not formed and so we see the distributions drop sharply to zero at lower masses than our fiducial results.

@@

\begin{figure}[b]
    \centering
    \includegraphics[width=\columnwidth]{../figures/BH_mass_dist_simple_mw.pdf}
    \caption{As Fig.~\ref{fig:fiducial_pdf_distributions} (top left panel), but for the Milky Way model used in \citet{Breivik+2020}.}
    \label{fig:bh_mass_simple_mw}
\end{figure}

>>>>

\subsection{Assessing the impact of Milky Way model choices}
In this section, we repeat our main analysis but instead apply a simpler model for the Milky Way in order to assess the effect of using a metallicity-dependent Milky Way model. For this purpose, we use model for the Milky Way used in \citet{Breivik+2020} as this is representative of the models used in most previous works.

Their model can be summarised as follows: the Milky Way is assumed to comprise of three components, a thin disc, a thick disc and a bulge. The spatial distributions and relative masses for these components are given in \citet{McMillan+2011}. \citet{Breivik+2020} assume constant star formation over 10 Gyr for the thin disc, a 1 Gyr burst of star formation 11 Gyr ago for the thick disc and a 1 Gyr burst of star formation 10 Gyr ago for the bulge. A major difference is that only two metallicities are used and they are assigned independent of age or position. Binaries formed in the thin disc and bulge are assumed to have a metallicity of $Z = 0.02$ and those formed in the thick disc are assumed to have $Z = 0.003$.

We show this model in Fig.~\ref{fig:simple_mw} in the same form as Fig.~\ref{fig:galaxy_schematic} for ease of comparison between our models. The two main differences we can see in these plots are that the \citet{Breivik+2020} model is more centrally concentrated and only has two fixed metallicity populations. In addition, though it can't be seen in these plots, the simpler prescriptions for the star formation histories mean that the overall star formation history is highly discontinuous at $\tau = 9 \unit{Gyr}$ and significantly more star formation occurs from $\tau = 9 \unit{Gyr}$ to $\tau = 11 \unit{Gyr}$.

@@

We find that when applying this simpler Milky Way model and our fiducial physics assumptions (model \modFid{}), the expected number of detections for BHBHs, BHNSs and NSNSs for a 4-year LISA mission is $39$, $39$ and $14$ respectively. Thus the BHBH and BHNS detection rates are only marginally increased from our main findings, but the NSNS detection is overestimated by nearly a factor of 2.

Moreover, the distribution of parameters within the population, particularly the mass distributions, are notably disparate. By using only two fixed metallicity populations, unphysical artifacts are introduced into distribution of DCO masses (Kummer at al. (in prep)). For example, in Fig.~\ref{fig:bh_mass_simple_mw}, we show the black hole mass distribution produced by the simulation using the simple Milky Way model. Despite the fact that these KDEs use the same bandwidth as Fig.~\ref{fig:fiducial_pdf_distributions}, the distributions show many more sharp transitions, which is a result of pileups occurring at specific masses for specific metallicities. Moreover, the lack of lower metallicities systems means that higher mass systems are not formed and so we see the distributions do not include a high mass tail such as in our fiducial results.

@@

Overall, we find that previous studies that use Milky Way models analogous to this simpler model may significantly overestimate the LISA NSNS detection rate as well as contain unphysical artifacts in their parameter distributions.

\begin{figure}[h]
    \centering
    \includegraphics[width=\columnwidth]{../figures/BH_mass_dist_simple_mw.pdf}
    \caption{As Fig.~\ref{fig:fiducial_pdf_distributions} (top left panel), but for the Milky Way model used in \citet{Breivik+2020}.}
    \label{fig:bh_mass_simple_mw}
\end{figure}
